---
title: "Coursera - Developing Data Projects - Course Project - Diamonds"
author: "Anders Molven Larsen"
date: "14 December 2017"
output: ioslides_presentation
---
## Overview

```{r, echo = FALSE}
library(ggplot2)
data(diamonds)
```

This was built as part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

The app developed as part of this assignment can be found at: https://darksyde98.shinyapps.io/diamonds/

The Github repository where the code and information is stored: https://github.com/Darksyde98/diamondapp

## Application Functionality

You are first asked to choose a number of diamonds to sample from 1 to the full number of 53,940 diamonds in the dataset.

Secondly you are asked to choose x and y values for the plot followed by color to separate the plot points.

The range of options are: ***carat***, ***cut***, ***color***, ***clarity***, ***depth***, ***table*** and ***price***.

Next you can choose jitter to avoid overplotting and smooth to add a smooth line to each plot.

Finally you can set facets rows and columns to plot multiple values across several plots.

## Diamonds data set

The app offers a simple way to explore and visualize the diamonds dataset found in ggplot2. This dataset is a collection of over 50,000 diamonds recorded with several variables that can be explored in this app.

```{r, echo = FALSE}
summary(diamonds)
```

## Data Plot

```{r}
g <- ggplot(data = diamonds, aes(x = carat, y = price)) +
        geom_point(inherit.aes = TRUE, aes(col = cut)) +
        facet_grid(. ~ color)
       
g
```


